\documentclass{resume}
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage[svgnames]{xcolor}
\usepackage{hyperref}
\hypersetup{%
  colorlinks=true,          % hyperlinks
  allcolors=DarkRed,%
  pdfborderstyle={/S/U/W 1} % border style will be underline of width 1pt
}
\usepackage{tabularx}

\usepackage{vwcol}
\usepackage{natbib}
\usepackage{cfr-lm}         % make old style numbers default
\usepackage{graphicx}
\usepackage{titlesec}
\titlespacing*{\subsection}{0pt}{0.5em}{0.2em} % Adjust the spacing as needed
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE SECTION

\begin{center}
    \name{Mike Mcrae}
\end{center}
\begin{content}
    \begin{tabularx}{\textwidth}{l @{\hspace{7cm}} X} % Adjust hspace to control distance
        {\bf Business Address} & \textbf{Web:} \href{https://mike-mcrae.github.io/}{https://mike-mcrae.github.io/} \\
        {Department of Economics} & \textbf{Mail:} \href{mailto://mcraemi@tcd.ie}{mcraemi@tcd.ie} \\
        {Trinity College Dublin} & \textbf{Citizenship:} Australian \\ 
        {Arts Building, College Green} &  \\
        {Dublin 2, Ireland} & \\
    \end{tabularx}
\end{content}


\sectionlineskip
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION 
\section{Research Fields} 
\begin{content}
    {\bf Primary} {Applied Microeconomics}
    
    {\bf Specific} {Media Economics, Political Economy, Evolution of norms, Economics of AI}    
\sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION 
\section{Education} 
\begin{content}
    {P.hD. in Economics, Trinity College Dublin} \hfill {\bf 2022 - 2025(Expected)} \\
    {M.Sc. in Economics, Trinity College Dublin (Distinction, First Place)} \hfill {\bf 2021 - 2022} \\
    {P.G. Diploma in Economics, University of New England (1st Class)} \hfill {\bf 2019} \\
    {B.Comm. in Economics \& Marketing, University of Sydney (1st Class)} \hfill {\bf 2014 - 2016} \\
\sectionlineskip
\end{content}
\vspace{-3\medskipamount}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH EXPERIENCE
\section{Work in Progress}
\begin{content}
	{``Black by Popular Demand - Media Competition and the Evolution of a Social Norm''}\\
	{``Vertical Governance of Online Speech: Evidence from Google’s Moderation Mandate"}\\
	{``From the Pulpit to the Polls: The Electoral Consequences of Christian Talk Radio"}\\
	{``Selective Science: How Media Bias Shapes Climate Change Narratives'' (with M. Pograxha)}\\
	{``When to baseline? - The impact of lottery allocation on household outcomes in a highly vulnerable setting'' (with C. M. Fernandez, A. Guariso, M. Holmlund, T. Mitchell, and C. Newman)}\\
\sectionlineskip
\end{content}
\vspace{-3\medskipamount}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION 
\section{Conferences, Seminars and Workshops} 
\begin{content}
    {29th Annual SIOE Conference (Sydney, Australia)} \hfill {\bf 2025} \\
    {3rd IFN Workshop in Economic History (Uppsala, Sweden)} \hfill {\bf 2025} \\
    {Text-as-Data in Economics Workshop (Lancaster University)} \hfill {\bf 2025} \\
    {9th Monash-Paris-Warwick-Zurich CEPR Text-as-Data Workshop (Online)} \hfill {\bf 2025} \\
    {Irish Economics Association Annual Coneference} \hfill {\bf 2022, 2023 \& 2025} \\
    {Irish Postgraduate and Early Career Economics Workshop} \hfill {\bf 2023}\\
    {Royal Economics Society Annual Conference} \hfill {\bf 2023} \\
\sectionlineskip
\end{content}
\vspace{-3\medskipamount}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AWARDS
%\section{Awards \& Grants}
%\begin{content}
%    {\raggedleft \textbf{Grants} \par} % Right-aligned subsection title
%    \prize[s]{Grattan Scholarship}{2022-2025}{- Full funding - PhD in Economics. €10,000 research fund.}\\
%    \prize[s]{TRISS Research Fellowship}{2023}{- Impactful research fund, TCD. €1,000 research fund.}\\
%    \prize[s]{Global Excellence Postgraduate Scholarship}{2021-2022}{- Tuition waiver - M.Sc. in Economics, TCD. }
%   {\raggedleft \makebox[2cm]{\hrulefill} \\ \textbf{Teaching} \par} % Right-aligned subsection title
%    \prize[s]{Dermott McAleese Teaching Assistant Award}{2023}{- Winner - Excellence in teaching and student support.}\\
%   {\raggedleft \makebox[2cm]{\hrulefill} \\ \textbf{Academic} \par} % Right-aligned subsection title
%    \prize[s]{Terence Gorman Award}{2022}{- 1st in Programme - M.Sc. (Economics) - Trinity College Dublin}\\
%    \prize[s]{IPSOS Market Research Prize}{2017}{- Impactful Market Research - The University of Sydney}\\
%    \prize[s]{Academic Merit Prizes}{2015, 2016}{- 1st in Class - The University of Sydney}\\
%    % Teaching with line above
%
%    % Grants with line above
%\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AWARDS
\section{Awards \& Grants}
\begin{content}
    {\raggedleft \textbf{\underline{Grants}}\par}
    \vspace{-0.2cm}
    \prize[s]{Grattan Scholarship}{2022-2025}{Full funding for PhD in Economics. €10,000 research fund.}\\
    \prize[s]{TRISS Research Fellowship}{2023 \& 2025}{Impactful research fund, TCD. €3,000 research fund.}\\
    \prize[s]{Global Excellence Postgraduate Scholarship}{2021-2022}{Tuition waiver for M.Sc. in Economics, TCD.}\\
    {\raggedleft \textbf{\underline{Teaching}}\par}
    \vspace{-0.2cm}
    \prize[s]{Dermott McAleese Teaching Assistant Award}{2023}{Winner for excellence in teaching and student support.}\\
    {\raggedleft \textbf{\underline{Academic}}\par}
    \vspace{-0.2cm}
    \prize[s]{Terence Gorman Award}{2022}{1st in Programme, M.Sc. (Economics), Trinity College Dublin.}\\
    \prize[s]{IPSOS Market Research Prize}{2017}{Impactful Market Research, The University of Sydney.}\\
    \prize[s]{Academic Merit Prizes}{2015, 2016}{1st in Class, The University of Sydney.}
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROJECTS
\section{Teaching} 
\begin{content}
	\prize[s]{Economics I (Undergraduate)}{2025}{- Lecturer, Maynooth}\\
	\prize[s]{Econometrics I (Undergraduate)}{2024}{- Lecturer, TCD}\\
	\prize[s]{Econometrics I and II (Undergraduate)}{2022-2024}{- Teaching Assistant, TCD}\\
	\prize[s]{Masters Thesis supervision}{2023-2024}{- M.Sc in Economics, TCD}\\
	\prize[s]{Econometrics (Masters)}{2021}{- Teaching Assistant, TCD}\\
	\prize[s]{Mathematical and Statistical Methods B (Undergraduate)}{2021}{- Teaching Assistant, TCD}\\
	\prize[s]{Microeconomics I \& II (Undergraduate)}{2015-2017}{- Teaching Assistant, USYD}\\
	\prize[s]{Econometrics I (Undergraduate)}{2015-2017}{- Teaching Assistant, USYD}\\
	\prize[s]{Macroeconomics II (Undergraduate)}{2015-2017}{- Teaching Assistant, USYD}\\
   \sectionlineskip    
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TECHNICAL SKILLS
\section{Technical Skills}
\begin{content}
    \begin{tabular}{ @{} >{\bf}l @{\hspace{6ex}} l }
        Programming Languages & Python, Stata, R, QGIS, PostgreSQL  \\
        Practical Applications & Machine Learning,  Spatial Data Analysis, Quantitative Text Analysis\\
    \end{tabular}
\sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% COURSE WORK
\section{References}
\begin{tabular}{l l l}
        {\bf Carol Newman} & {\bf Tara Mitchell} & {\bf Nicola Mastrorocco} \\[.5\smallskipamount]
        Trinity College Dublin &  Trinity College Dublin & University of Bologna \\ 
        {\href{mailto://newmanc@tcd.ie}{newmanc@tcd.ie}} & {\href{mailto://mitchet@tcd.ie}{mitchet@tcd.ie}} & {\href{mailto://nicola.mastrorocco@unibo.it }{nicola.mastrorocco@unibo.it }} \\
\end{tabular}

\end{document}
